---
title: "Modeling COVID-19 transmission among Shincheonji community members and in Daegu City"
chunk_output_type: console
editor_options:
  chunk_output_type: console
output:
  html_document: default
  pdf_document: default
---



### Daegu epidemic curve
```{r}
library( readxl )
library( tidyverse )
library( lubridate )
d1 <- read_xlsx( "data/covid_daegu.xlsx", "incidence")
d <- d1[,1:5]
d$date <- ymd(d$date)
names( d ) <- c( "date", "daily_total", "daily_shincheonji", "total", "shincheonji" )
# dd <- tidyr::gather( d, key, val, -c(date, daily_total, daily_shincheonji, Total ) )

dfs <- ymd("2020-02-07") # date first symptom
dfc <- ymd("2020-02-18") # date first confirm
dpc <- ymd("2020-02-22") #date policy change
dg <- c(ymd("2020-02-15"), ymd("2020-03-01"), ymd("2020-03-15"), ymd("2020-04-01")) # regular dates for guidance


p <- ggplot( d ) +
  geom_bar( aes( date, total), stat="identity", fill=NA, color="black") +
  geom_bar( aes( date, shincheonji), stat="identity", fill="grey50") +
  scale_y_continuous( limits=c(0,8000) ) +
  scale_x_date( limits=c(ymd("2020-02-05"), max(d$date)+1 ), 
                labels=c(dfs, dfc, dpc, dg), 
                breaks=c(dfs, dfc, dpc, dg), 
                date_labels = "%b %d") +
  labs(y="Cumulative number of cases", x="Date" ) +
  annotate( "rect", xmin=max(d$date)-6, xmax=max(d$date)-5, ymin = 7900, ymax = 8000, fill=NA, color="black" ) +
  annotate( "rect", xmin=max(d$date)-6, xmax=max(d$date)-5, ymin = 7700, ymax = 7800, fill="grey50" ) + 
  annotate( "text", x = max(d$date)-3, y=c(7950,7750), label=c("Total", "Shincheonji"), hjust=0, size=2.5 ) +
  theme_classic( base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust=1), panel.grid.major=element_line("grey90") )

p  
# Descriptions about the government policy was then added to the figure using MS Powerpoint 
```


### Missing data imputation
```{r}
library(imputeTS)
library(zoo)
library(tidyverse)
library(magrittr)
library(lubridate)

d1 <- read_xlsx( "data/covid_daegu.xlsx", "incidence")
d2 <- d1[,1:5]
d2$date <- ymd(d2$date)
names( d2 ) <- c( "date", "daily_total", "daily_shincheonji", "total", "shincheonji" )

shin <- na.spline( d2$shincheonji )
# shin <- na_interpolation (d2$shincheonji)
# shin <- na_kalman(d2$shincheonji)

d <- data.frame( tot=d2$total, shin=shin, low=d2$total-shin )
nr<-nrow(d)
daily_tot <- d$tot[2:nr] - d$tot[1:(nr-1)]
daily_low <- d$low[2:nr] - d$low[1:(nr-1)]
daily_shin <- d$shin[2:nr] - d$shin[1:(nr-1)]

dd <- cbind(d, data.frame(daily_tot=c(d$tot[1],daily_tot),daily_shin=c(d$shin[1],daily_shin),daily_low=c(d$low[1],daily_low) ))


dd %<>% mutate( daily_tot_new = ifelse( daily_low < 0, daily_shin, daily_tot ),
               daily_shin_new = ifelse( daily_low < 0, daily_tot, daily_shin ), 
               daily_low_new = ifelse( daily_low < 0, daily_shin - daily_tot, daily_low ) )

dd %<>% mutate( daily_tot_new = ifelse( daily_shin_new < 0, daily_low_new, daily_tot_new ),
               daily_shin_new = ifelse( daily_shin_new < 0, daily_low_new - daily_tot_new, daily_shin_new ), 
               daily_low_new = ifelse( daily_shin_new < 0, daily_tot_new, daily_low_new ) )

dates <- data.frame(date=seq( ymd("2020-02-18"), by="day", length.out=nrow(dd) ))
ddd <- cbind(dates,dd)
names(ddd) <- c( "date", "cumul_total", "cumul_shincheonji", "cumul_low", "d_tot", "d_shin", "d_low", "daily_total", "daily_shincheonji", "daily_low" )
ddd$cumul_total <- cumsum( ddd$daily_total )
ddd$cumul_shincheonji <- cumsum( ddd$daily_shincheonji )
ddd$cumul_low <- cumsum( ddd$daily_low )

write_csv( ddd, "outputs/DAT_Imputed.csv" )

```


### Missing data imputation figure 
```{r}
library(imputeTS)
library(tidyverse)
library(readxl)
library(lubridate)

d1 <- read_xlsx( "data/covid_daegu.xlsx", "incidence")
d <- d1[,1:5]
d$date <- ymd(d$date)
names( d ) <- c( "date", "daily_total", "daily_shincheonji", "Total", "Shincheonji" )

p <- ggplot( d ) +
  geom_bar( aes( date, Total), stat="identity", fill=NA, color="black") +
  geom_bar( aes( date, Shincheonji), stat="identity", fill="grey50") +
  scale_y_continuous( limits=c(0,8000) ) +
  labs( y="Cumulative number of cases", x="Date" ) +
  annotate( "rect", xmin=max(d$date)-9, xmax=max(d$date)-8, ymin=7900, ymax=8000, fill=NA, color="black" ) +
  annotate( "rect", xmin=max(d$date)-9, xmax=max(d$date)-8, ymin=7500, ymax=7600, fill="grey50", color="grey50" ) + 
  annotate( "text", x = max(d$date)-6, y=c(7950,7550), 
            label=c("Total", "Shincheonji"), hjust=0, size=3 ) +
  scale_x_date( date_labels = "%b %d", 
                labels=seq( ymd("2020-02-15"), ymd("2020-03-31"), length.out=10), 
                breaks=seq( ymd("2020-02-15"), ymd("2020-03-31"), length.out=10) )+
  theme(axis.text.x = element_text(angle = 45, hjust=1), panel.grid.major=element_line("grey90") ) +
  theme_bw(base_size = 10)

p  

ggsave( "plots/before_impute.png", p, width=3.4, height=2.7, units="in" )
# d$Shincheonji <- na.spline(d$Shincheonji)
ggsave( "plots/after_impute.png", p, width=3.4, height=2.7, units="in" )

```


### Fitting via Approximate Bayesian Computation Sequential Monte Carlo
```{r}
rm(list=ls())
library(tmvtnorm)
library(truncnorm)
library(Rcpp) 
sourceCpp( "models/seir_2grp_tauleap_cpp.cpp" )
source( "func/read_inputs.R" )
source( "func/load_data.R" )  
source( "func/model_functions.R" )
# params_est <- readin_params( "inputs/par_fa_010.csv", cont_mat="inputs/cont_mat_3grp.csv" )
params_est <- readin_params( "inputs/par.csv", cont_mat="inputs/cont_mat_2grp.csv" )
params <- params_est[["params"]]

set.seed(123)
max_diff_high <- sqrt( sum( (2*DAT$daily_shincheonji)^2, na.rm=T ) )
max_diff_low <- sqrt( sum( (2*DAT$daily_low)^2, na.rm=T ) )

epsilon_inc_high <- seq( max_diff_high, round(0.06*max_diff_high), length.out=20 )
epsilon_inc_low <- seq( max_diff_low, round(0.06*max_diff_low), length.out=20 )

G <- length( epsilon_inc_high )# Generations of SMC
N <- 200 # Number of particles
n <- 3 # Number of simulations for each parameter set (since it's a deterministic model)
lb <- c( 1,   1e-3, 1e-3,  1,  1e-6, 1  )
ub <- c( 15,  10,   10,   20,   0.5,  30 )
np <- length( lb ) #number of parameters
res_old <- matrix( ncol=np, nrow=N ) #to store SMC samples for the parameters
res_new <- matrix( ncol=np, nrow=N )
# Empty vectors to store weights
w_old <- matrix( ncol=1, nrow=N )
w_new <- matrix( ncol=1, nrow=N )

tbegin <- Sys.time()
tstamp <- format( tbegin, "%m%dT%H%M" )
simlog <- file( "outputs/simlog.log" )

for( g in 1:G ){
  i <- 1
    while( i <= N ){
        if( g == 1 ){ # start using prior distributions
            par <- runif( np, min=lb, max=ub )
            # par <- c( 8, 2, 0.4, 10, 1e-4, 14 )
            R01 <- par[1]
            R02 <- par[2]
            final_R01 <- par[3]
            final_R02 <- par[3]
            I01 <- (1-params$frac_asymp) * par[4]
            A01 <- params$frac_asymp * par[4]
            frac_mix <- par[5]
            dur_intervention <- par[6]
            
        } else {
            p <- sample( seq(1,N), 1, prob=w_old )
            par <- rK( res_old[ p, ], sigma )#  Select particle from previous generation
            R01 <- par[1]
            R02 <- par[2]
            final_R01 <- par[3]
            final_R02 <- par[3]
            I01 <- (1-params$frac_asymp) * par[4]
            A01 <- params$frac_asymp * par[4]
            frac_mix <- par[5]
            dur_intervention <- par[6]
        }
        #  Test if prior non zero
        if( prior_non_zero( c( R01, R02, final_R01, I01, frac_mix, dur_intervention ) ) &
            final_R01 < R01 & final_R02 < R02 ) {
            # Set number of accepted simulations to zero
            m <- 0
            distance <- matrix( ncol=2, nrow=n ) # # data = 2
            for( j in 1:n ){
                params$R01 <- R01
                params$R02 <- R02
                params$final_R02 <- final_R02
                params$final_R01 <- final_R01
                params$init$I1 <- round(I01)
                params$init$A1 <- round(A01)
                params$init$S1 <- params$pop_high - I01
                params$cm <- c(1-frac_mix, frac_mix, frac_mix, 1-frac_mix)
                params$time_intervention_stop <- params$time_intervention_start + dur_intervention
                
                Dstar <- run_model_tauleap( params )     
                calc_dist <- calc_distance( Dstar[[1]], Dstar[[2]] )
                distance[ j, ] <- calc_dist    
                if( (calc_dist[1] <= epsilon_inc_high[g]) & (calc_dist[2] <= epsilon_inc_low[g]) ){
                    m <- m + 1
                }
            }   
            if( m > 0 ){
                res_new[ i, ]<- c( R01, R02, final_R01, I01, frac_mix, dur_intervention )  # Store results
                w1 <- prod( sapply(1:length(ub), function(x) dunif( res_new[ i, x ], min=lb[x], max=ub[x] ) ) ) # Calculate weights
                if( g==1 ){
                    w2 <- 1
                } else {
                    w2 <- sum( sapply( 1:N, function(x) w_old[x]* dtmvnorm( res_new[ i, ], res_old[ x,], sigma, lb, ub ) ) )
                }
                w_new[ i ] <- (m/n)*w1/w2
                
                if( i%%20 == 0 ){# to monitor the progress
                  tnow <-  Sys.time()
                  telapsed <- round( difftime( tnow, tbegin, units = "mins")[[1]], digits=1 )
                  log <- paste0( 'Gen=', g, ", Particle=", i, ", time=", format( tnow, "%H:%M:%S" ), ", minutes elapsed=", telapsed )
                  print( log )
                  cat( log, file = simlog, append=TRUE ) # creates file and writes to it

                }
                i <- i + 1
            }
        } 
    }
    
    sigma <- cov( res_new )
    res_old <- res_new
    w_old <- w_new / sum( w_new )

    write.csv( res_new, file=paste0("outputs/tauleap_", g, ".csv"), row.names=FALSE )
}

write.csv( res_new, paste0("outputs/samples_", tstamp, ".csv"), row.names=FALSE  )
saveRDS( params, paste0("outputs/params_", tstamp, ".rds" ) )
saveRDS( seir_2grp_tauleap, paste0("outputs/seir_2grp_tauleap_", tstamp, ".rds") )
```


### Run the model and save the results 
```{r}
# tstamp <- "0522T1228"
# tstamp <- "0614T2133"
tstamp <- "0624T2024"

library( Rcpp )
library( tidyverse )
library( lubridate )
sourceCpp( "models/seir_2grp_tauleap_cpp.cpp" )
source( "func/read_inputs.R" )
source( "func/load_data.R" )
source( "func/model_functions.R" )

par <- read_csv( paste0( "outputs/samples_", tstamp, ".csv" ) ) ## estimated params
DAT <- read_csv( paste0( "outputs/DAT_", tstamp, ".csv" ) )
params <- readRDS( paste0( "outputs/params_", tstamp, ".rds" ) )
set.seed(123)

# params_est <- readin_params( "inputs/par.csv", cont_mat="inputs/cont_mat_2grp.csv" )
# params <- params_est[["params"]]

## alternative definitions (tstamp <- "0614T2133")
# params$delta <- 1/((1/params$delta) - 2.2)
# params$rate_isol <- 1/((1/params$rate_isol) + 2.2)

nday <- as.integer(params[["ndays"]])

res_high <- as.data.frame( matrix(nrow=nday, ncol=(nrow(par)) ) )
res_low <- as.data.frame( matrix(nrow=nday, ncol=(nrow(par)) ) )
I_high <- as.data.frame( matrix(nrow=nday, ncol=(nrow(par)) ) )
I_low <- as.data.frame( matrix(nrow=nday, ncol=(nrow(par)) ) )
CI_high <- as.data.frame( matrix(nrow=nday, ncol=(nrow(par)) ) )
CI_low <- as.data.frame( matrix(nrow=nday, ncol=(nrow(par)) ) )

## dates on the first column
dates <- seq( ymd("2020-02-07"), by="day", length.out=nrow(res_high) )
res_high[,1] <- dates
res_low[,1] <- dates

for( ii in seq_len(nrow(par)) ){

  params$R01 <- as.double( par[ ii, 1 ] )
  params$R02 <- as.double( par[ ii, 2 ] )
  params$final_R01 <- as.double( par[ ii, 3 ] )
  params$final_R02 <-  as.double( par[ ii, 3 ] )
  I01 <- (1-params$frac_asymp) * as.double( par[ ii, 4 ] )
  A01 <- params$frac_asymp * as.double( par[ ii, 4 ] )
  params$init$I1 <- round( I01 )
  params$init$A1 <- round( A01 )
  params$init$S1 <- params$pop_high - I01
  mix <- as.double( par[ ii, 5 ] )
  params$cm <- c( 1 - mix, mix, mix, 1-mix )
  params$time_intervention_stop <- params$time_intervention_start + as.double( par[ ii, 6 ] )
 
  res <- seir_2grp_tauleap( params )

  res_high[ , ii ] <- res$X1[ params$day_filter ]
  res_low[ , ii ] <- res$X2[ params$day_filter ]
  I_high[ , ii ] <- res$I1[ params$day_filter ]
  CI_high[ , ii ] <- res$CI1[ params$day_filter ]
  I_low[ , ii ] <- res$I2[ params$day_filter ]
  CI_low[ , ii ] <- res$CI2[ params$day_filter ]

}

### cumulative incidence
nc <- ncol( res_high )
nr <- nrow( res_high )

res_tot <- res_high + res_low # excluding dates on the first column
pr <- c(0.025, 0.25, 0.5, 0.75, 0.975)

inc_high <- CI_high
inc_low <- CI_low
inc_low <- CI_low[ 2:nr, ] - CI_low[ 1:(nr-1), ]
inc_high <- CI_high[ 2:nr, ] - CI_high[ 1:(nr-1), ]

res_tot_summary = apply( res_tot, 1, quantile, probs=pr )
res_high_summary = apply( res_high, 1, quantile, probs=pr )
res_low_summary = apply( res_low, 1, quantile, probs=pr )

inc_high_summary = apply( inc_high, 1, quantile, probs=pr )
inc_low_summary = apply( inc_low, 1, quantile, probs=pr )

sim <- data.frame(rbind(
    data.frame(pop = 1, date=dates, q025=res_high_summary[1,],
               q250=res_high_summary[2,], q500=res_high_summary[3,],
               q750=res_high_summary[4,], q975=res_high_summary[5,]),
    data.frame(pop = 2, date=dates, q025=res_low_summary[1,],
               q250=res_low_summary[2,], q500=res_low_summary[3,],
               q750=res_low_summary[4,], q975=res_low_summary[5,]),
    data.frame(pop = 3, date=dates, q025=res_tot_summary[1,],
               q250=res_tot_summary[2,], q500=res_tot_summary[3,],
               q750=res_tot_summary[4,], q975=res_tot_summary[5,])))

daily_low <- res_low
daily_low[ 2:nr, ] <- res_low[ 2:nr, ] - res_low[ 1:(nr-1), ]
daily_high <- res_high
daily_high[ 2:nr, ] <- res_high[ 2:nr, ] - res_high[ 1:(nr-1), ]

d_high_summary = apply( daily_high, 1, quantile, probs=pr )
d_low_summary = apply( daily_low, 1, quantile, probs=pr )

sim_daily <- data.frame(rbind(
    data.frame(pop = 1, date=dates, q025=d_high_summary[1,],
               q250=d_high_summary[2,], q500=d_high_summary[3,],
               q750=d_high_summary[4,], q975=d_high_summary[5,]),
    data.frame(pop = 2, date=dates, q025=d_low_summary[1,],
               q250=d_low_summary[2,], q500=d_low_summary[3,],
               q750=d_low_summary[4,], q975=d_low_summary[5,])　) )

sim_daily$pop <- factor( sim_daily$pop, labels=c("High risk", "Low risk") )
sim$pop <- factor( sim$pop, labels=c("High risk", "Low risk", "Total") )

# saveRDS( sim, paste0("outputs/sim_", tstamp, ".rds" ) )
# saveRDS( sim_daily, paste0("outputs/sim_daily_", tstamp, ".rds" ) )

```

### Figure of model simulation based on 
```{r}
library(ggplot2)
library(lubridate)
library(readxl)
sim <- readRDS( paste0("outputs/sim_", tstamp, ".rds" ) )
sim_daily <- readRDS( paste0("outputs/sim_", tstamp, ".rds" ) )

theme_set( theme_bw(base_size = 12) )
total <- dplyr::filter( sim, pop == "Total" )
high <- dplyr::filter( sim, pop == "High risk" )

d0 <- read_xlsx( "data/covid_daegu.xlsx", "incidence")
d <- d0[,1:5]
d$date <- ymd(d$date)
names( d ) <- c( "date", "daily_total", "daily_shincheonji", "Total", "Shincheonji" )
# dd <- tidyr::gather( d, key, val, -c(date, daily_total, daily_shincheonji, Total ) )
dfs <- ymd("2020-02-07") # date first symptom
dfc <- ymd("2020-02-18") # date first confirm
dpc <- ymd("2020-02-22") #date policy change
dg <- c(ymd("2020-02-15"), ymd("2020-03-01"), ymd("2020-03-15"), ymd("2020-04-01")) # regular dates for guidance
xd <- ymd("2020-02-07")
yy <- 7800 

plt <- ggplot( d ) +
  geom_bar( aes( date, Total), stat="identity", fill=NA, color="black") +
  geom_bar( aes( date, Shincheonji), stat="identity", fill="grey50") +
  # geom_ribbon( data=total, aes(x=date, ymin=q025, ymax=q975), fill="steelblue",  alpha=0.2, inherit.aes=F ) +
  geom_ribbon( data=total, aes(x=date, ymin=q250, ymax=q750), fill="steelblue",  alpha=0.4, inherit.aes=F ) +
  geom_line( data=total, aes(date, q500), color="steelblue", size=1.2, inherit.aes=F ) +
  # geom_ribbon( data=high, aes(x=date, ymin=q025, ymax=q975), fill="darkred",  alpha=0.2, inherit.aes=F ) +
  geom_ribbon( data=high, aes(x=date, ymin=q250, ymax=q750), fill="darkred",  alpha=0.4, inherit.aes=F ) +
  geom_line( data=high, aes(date, q500), color="darkred", size=1.2, inherit.aes=F ) +
  # scale_y_continuous( limits=c(0,8000)) +
  scale_x_date( limits=c(ymd("2020-02-05"), max(d$date)+1 ), 
                labels=c(dfs, dfc, dpc, dg), 
                breaks=c(dfs, dfc, dpc, dg), 
                date_labels = "%b %d") +
  labs(y="Cumulative confirmed cases", x="Date", size=7 ) +
  theme( axis.text.x = element_text(angle = 45, hjust=1) ) +
  theme( axis.title.y = element_text(size=11) ) +

  annotate( "rect", xmin=xd, xmax=xd+2, ymin=yy, ymax=yy+200, alpha=0.4, fill="steelblue") +
  annotate( "segment", x=xd, xend=xd+2, y=yy+100, yend=yy+100, size=1, color="steelblue" ) +
  annotate( "rect", xmin=xd, xmax=xd+2, ymin=yy-300, ymax=yy-100, alpha=0.4, fill="darkred") +
  annotate( "segment", x=xd, xend=xd+2, y=yy-200, yend=yy-200, size=1, color="darkred" ) +
  annotate( "text", x=xd+3, y=yy+100, size=1.5, label="Total (model)", hjust=0, vjust=0.5 ) +
  annotate( "text", x=xd+3, y=yy-200, size=1.5, label="Shincheonji (model)", hjust=0, vjust=0.5 ) + 
  
  annotate( "rect", xmin=xd, xmax=xd+2, ymin=yy-600, ymax=yy-400, fill=NA, color="black" ) +
  annotate( "rect", xmin=xd, xmax=xd+2, ymin=yy-900, ymax=yy-700, fill="grey50", color="black" ) +
  annotate( "text", x=xd+3, y=yy-500, size=1.5, label="Total (data)", hjust=0, vjust=0.5 ) +
  annotate( "text", x=xd+3, y=yy-800, size=1.5, label="Shincheonji (data)", hjust=0, vjust=0.5 ) +
  annotate( "text", x=ymd("2020-3-31"), y=8000, label="A", hjust=0, vjust=0.5, size=3 )
 
plt

# ggsave( paste0("plots/cumul_data_model_", tstamp, ".png"), plt, width=3.4, height=2.7, units="in" )
```



### POSTERIOR distribution 
```{r}
tstamp <- "0624T2024" 
# tstamp <- "0614T1722"
p <- read.csv( paste0("outputs/samples_", tstamp, ".csv") )
params <- readRDS( paste0( "outputs/params_", tstamp, ".rds" ) )

## This is to calculate actual R0 based on the 
beta1 <- p$V1/(1/(params$gamma+params$rate_isol))
beta2 <- p$V2/(1/(params$gamma+params$rate_isol))
betastar <- p$V3/(1/(params$gamma+params$rate_isol))

R01 <- beta1*(1/(params$delta2)+ 1/(params$gamma+params$rate_isol))
R02 <- beta2*(1/(params$delta2)+ 1/(params$gamma+params$rate_isol))                          
Rstar <- betastar*(1/(params$delta2)+ 1/(params$gamma+params$rate_isol))      

p$V1 <- R01
p$V2 <- R02
p$V3 <- Rstar

library(ggplot2)
theme_set(theme_bw(base_size = 12))

pr = c( 0.025, 0.25, 0.5, 0.75, 0.975 )
quantile( p$V1, probs=pr )
quantile( p$V2, probs=pr )
quantile( p$V3, probs=pr )
quantile( round(p$V4), probs=pr )
quantile( p$V5, probs=pr )
quantile( p$V6, probs=pr )

pq <- sapply( 1:6, function(x) quantile( p[,x], probs=pr ) )

d <- cbind( 
  data.frame( 
    par = c("R01", "R02", "Final_R0", "I0", "Mixing", "Intervention days"),
    id = (6-c(1, 2, 3, 4, 5, 6))),
  as.data.frame( t(pq) ) )

plt <- ggplot(d) +
  geom_segment( aes(y=`2.5%`, yend=`97.5%`, x=id, xend=id), size=1 ) +
  geom_segment( aes(y=`25%`, yend=`75%`, x=id, xend=id), size=1.6 ) +
  geom_point( aes(id, `50%`), size=2.2, color="red" ) +
  scale_x_continuous( name="Parameters",labels=c( expression(italic(d)), expression(italic(c)~"*"), expression(italic(I)[0]), expression(italic(R)~"*"), expression(italic(R)[0]^2), expression(italic(R)[0]^1)) ) + 
  scale_y_continuous( name="Value" ) +
  annotate( "text", x=5, y=15, label="B", hjust=0, vjust=0.5, size=3 ) +
  coord_flip() 

plt  
# ggsave(paste0( "plots/params_", tstamp, ".png"), plt, width=3.4, height=2.7, units="in" )


### correlation plot
library(ggplot2)
library(GGally)
theme_set(theme_bw(base_size=12))
plt <- ggpairs( p, 
         columnLabels=c( "italic(R)[0]^1", "italic(I)[0]", 'italic(c)~"*"', 'italic(R)~"*"', "italic(d)", "italic(R)[0]^2" ), 
         labeller = "label_parsed") 

# ggsave(paste0( "plots/params_coor_", tstamp, ".png"), plt, width=3.4*2, height=2.7*2, units="in" )
  # columnLabels = c( "italic(R)[0]^1", "italic(I)[0]", "italic(c)~\*", "italic(R)~\*", "italic(d)", "italic(R)[0]^2" ),


ggplot(p) +
  geom_histogram( aes(x=V1,y=..density..), fill="red", alpha=0.6 ) +
  labs( y="Density", x=expression(italic(R)[0]~"in"~"Shincheonji") ) +
  geom_density(aes(x=V1,y=..density..), size=1.0 ) +
  annotate( "text", x=min(p$V1), y=0.35, size=5, label="B", hjust=0, vjust=0.5 )

# ggsave(paste0( "plots/R0_shinchenji_", tstamp, ".png"), width=3.4*2, height=2.7*2, units="in" )

ggplot(p) +
  geom_histogram( aes(x=V6,y=..density..), fill="red", alpha=0.6 ) +
  labs( y="Density", x=expression(italic(R)[0]~"in"~"non-Shincheonji") ) +
  geom_density(aes(x=V6,y=..density..), size=1.0 ) +
  annotate( "text", x=min(p$V6), y=0.35, size=5, label="C", hjust=0, vjust=0.5 )

# ggsave(paste0( "plots/R0_non-shinchenji_", tstamp, ".png"), width=3.4*2, height=2.7*2, units="in" )

ggplot(p) +
  geom_histogram( aes(x=V2,y=..density..), fill="red", alpha=0.6 ) +
  labs( y="Density", x="Infected people on Feb 7" ) +
  geom_density(aes(x=V2,y=..density..), size=1.2 ) +
  annotate( "text", x=min(p$V2), y=0.15, size=5, label="D", hjust=0, vjust=0.5 )

# ggsave(paste0( "plots/Infecteds_Feb7_", tstamp, ".png"), width=3.4*2, height=2.7*2, units="in" )

ggplot(p) +
  geom_histogram( aes(x=V6,y=..density..), fill="blue", alpha=0.4 ) +
  labs(title="Non-Shincheonji", y="Density", x=expression(italic(R)[0]) ) +
  geom_density(aes(x=V6,y=..density..), size=1.0 ) +
  theme_bw(base_size = 14)
  # annotate( "text", x=min(p$V1), y=0.35, size=5, label="c", hjust=0, vjust=0.5 )

# ggsave(paste0( "plots/R0_non-shinchenji_", tstamp, ".png"), width=3.4*2, height=2.7*2, units="in" )



# hist( p$V1, breaks=10, ylab="Frequency", xlab="R01", main="R01" )
# hist( p$V2, breaks=10, ylab="Frequency", xlab="I0", main="Number of initially infectious people" )
# hist( p$V3, breaks=10, ylab="Frequency", xlab="Mixing proportion", main="Mixing proportion" )
# hist( p$V4, breaks=10, ylab="Frequency", xlab="Min_R0", main="R0 toward the end of the outbreak" )
# hist( p$V5, breaks=10, ylab="Frequency", xlab="Intervention days", main="Duration of intervention" )
# hist( p$V6, breaks=10, ylab="Frequency", xlab="R02", main="R02" )

library("bayesplot")
color_scheme_set("red")

names(p) = c("R01", "I0", "Mixing", "Final_R01", "Intervention days", "R02")

# mcmc_intervals( p, pars = c(expression(beta[1]), "I0", "mix", "t*", "daily_reduc"))
mcmc_pairs( p, pars = c("R01", "I0", "Mixing", "Final_R01", "Intervention days", "R02"),
            labels = c( expression(italic(R)[0]^1), expression(italic(I)[0]), expression(italic(c)~"*"), expression(italic(R)~"*"), expression(italic(d)), expression(italic(R)[0]^2) ),  
            off_diag_args = list(size=2, alpha=1/3) )

plt <- mcmc_pairs( p, pars = c( expression(italic(R)[0]^1), expression(italic(I)[0]), expression(italic(c)~"*"),  expression(italic(R)~"*"), expression(italic(d)), expression(italic(R)[0]^2) ),
                  off_diag_args = list(size=2, alpha=1/3) )

# ggsave(paste0( "plots/pairs_", tstamp, ".png"), p, width=3.4*4, height=2.7*4, units="in" )

p2 <- p[,1:2]
names(p2) = c("R01", "I0")
# mcmc_intervals( p, pars = c(expression(beta[1]), "I0", "mix", "t*", "daily_reduc"))
mcmc_pairs( p2, pars = c("R01", "I0"), 
            off_diag_args = list(size=2, alpha=1/3) )

# p <- mcmc_pairs( p, pars = c("beta1", "I0", "mix", "t*", "daily_reduc"),
#             off_diag_args = list(size=2, alpha=1/3) )
# plots <- p$bayesplots # modify each plot
# library(ggplot2)
# for( ii in seq_along(p) ){
#   plots[[ii]] <- plots[[ii]] + theme(text=element_text(size=12,  family="TT Arial"))
# }
# pp <- bayesplot_grid(plots = plots)
# tstamp <- format( Sys.time(), "%m%dT%H%M" )
# ggsave(paste0( "plots/pairs_", tstamp, ".png"), pp, width=3.4*2, height=2.7*2, units="in" )
```















### Sensitivity analysis 1 - fitting the model under the assumption that infected people become infectious 2-3 days prior to symptom onset
```{r}
rm(list=ls())
library(tmvtnorm)
library(truncnorm)
library(Rcpp) 
sourceCpp( "models/seir_2grp_tauleap_cpp.cpp" )
source( "func/read_inputs.R" )
source( "func/load_data.R" )  
source( "func/model_functions.R" )
# params_est <- readin_params( "inputs/par_fa_010.csv", cont_mat="inputs/cont_mat_3grp.csv" )
params_est <- readin_params( "inputs/par.csv", cont_mat="inputs/cont_mat_2grp.csv" )
params <- params_est[["params"]]
## sensitivity analysis
## latent stage becomes shorter by 2.2 days and time from becoming infectious to isolation increases by 2.2 days.
params$delta <- 1/((1/params$delta) - 2.2)
params$rate_isol <- 1/((1/params$rate_isol) + 2.2)
  
set.seed(123)
max_diff_high <- sqrt( sum( (2*DAT$daily_shincheonji)^2, na.rm=T ) )
max_diff_low <- sqrt( sum( (2*DAT$daily_low)^2, na.rm=T ) )

epsilon_inc_high <- seq( max_diff_high, round(0.06*max_diff_high), length.out=20 )
epsilon_inc_low <- seq( max_diff_low, round(0.06*max_diff_low), length.out=20 )

# epsilon_inc_high <- c( epsilon_inc_high[1:7], seq(epsilon_inc_high[8], epsilon_inc_high[10], length.out=10 ) )
# epsilon_inc_low <- c( epsilon_inc_low[1:7], seq(epsilon_inc_low[8], epsilon_inc_low[10], length.out=10 ) )

G <- length( epsilon_inc_high )# Generations of SMC
N <- 200 # Number of particles
n <- 3 # Number of simulations for each parameter set (since it's a deterministic model)
lb <- c( 1,   1, 1e-6, 1e-3,  1, 1e-3  )
ub <- c( 20, 50,  0.1,   10, 30,   20 )
np <- length( lb ) #number of parameters
res_old <- matrix( ncol=np, nrow=N ) #to store SMC samples for the parameters
res_new <- matrix( ncol=np, nrow=N )
# Empty vectors to store weights
w_old <- matrix( ncol=1, nrow=N )
w_new <- matrix( ncol=1, nrow=N )

tbegin <- Sys.time()
tstamp <- format( tbegin, "%m%dT%H%M" )
simlog <- file("outputs/simlog.log")

for( g in 1:G ){
  i <- 1
    while( i <= N ){
        if( g == 1 ){ # start using prior distributions
            par <- runif( np, min=lb, max=ub )
            R01 <- par[1]
            I01 <- (1-params$frac_asymp) * par[2]
            A01 <- params$frac_asymp * par[2]
            frac_mix <- par[3]
            final_R01 <- par[4]
            dur_intervention <- par[5]
            R02 <- par[6]
            final_R02 <- par[4]
            
        } else {
            p <- sample( seq(1,N), 1, prob=w_old )
            par <- rK( res_old[ p, ], sigma )#  Select particle from previous generation
            R01 <- par[1]
            I01 <- (1-params$frac_asymp) * par[2]
            A01 <- params$frac_asymp * par[2]
            frac_mix <- par[3]
            final_R01 <- par[4]
            dur_intervention <- par[5]
            R02 <- par[6]
            final_R02 <- par[4]
        }
        #  Test if prior non zero
        if( prior_non_zero( c( R01, I01, frac_mix, final_R01, dur_intervention, R02) ) &
            final_R01 < R01 & final_R02 < R02 ) {
            # Set number of accepted simulations to zero
            m <- 0
            distance <- matrix( ncol=2, nrow=n ) # # data = 2
            for( j in 1:n ){
                params$R01 <- R01
                params$init$I1 <- round(I01)
                params$init$A1 <- round(A01)
                params$init$S1 <- params$pop_high - I01
                params$cm <- c(1-frac_mix, frac_mix, frac_mix, 1-frac_mix)
                params$final_R01 <- final_R01
                params$time_intervention_stop <- params$time_intervention_start + dur_intervention
                params$R02 <- R02
                params$final_R02 <- final_R02
                
                Dstar <- run_model_tauleap( params )     
                calc_dist <- calc_distance( Dstar[[1]], Dstar[[2]] )
                distance[ j, ] <- calc_dist    
                if( (calc_dist[1] <= epsilon_inc_high[g]) & (calc_dist[2] <= epsilon_inc_low[g])){
                    m <- m + 1
                }
                # if( (calc_dist[1] + calc_dist[2]) <= (epsilon_inc_high[g] + epsilon_inc_low[g]) ){
                #     m <- m + 1
                # }
            }   
            if( m > 0 ){
                res_new[ i, ]<- c( R01, I01, frac_mix, final_R01, dur_intervention, R02 )   # Store results
                w1 <- prod( sapply(1:length(ub), function(x) dunif( res_new[ i, x ], min=lb[x], max=ub[x] ) ) ) # Calculate weights
                if( g==1 ){
                    w2 <- 1
                } else {
                    w2 <- sum( sapply( 1:N, function(x) w_old[x]* dtmvnorm( res_new[ i, ], res_old[ x,], sigma, lb, ub ) ) )
                }
                w_new[ i ] <- (m/n)*w1/w2
                
                if( i%%20 == 0 ){# to monitor the progress
                  tnow <-  Sys.time()
                  telapsed <- round( difftime( tnow, tbegin, units = "mins")[[1]], digits=1 )
                  log <- paste0( 'Gen=', g, ", Particle=", i, ", time=", format( tnow, "%H:%M:%S" ), ", minutes elapsed=", telapsed )
                  print( log )
                  cat( log, file = simlog, append=TRUE ) # creates file and writes to it

                }
                i <- i + 1
            }
        } 
    }
    
    sigma <- cov( res_new )
    res_old <- res_new
    w_old <- w_new / sum( w_new )

    write.csv( res_new, file=paste0("outputs/tauleap_", g, ".csv"), row.names=FALSE )
}

write.csv( res_new, paste0("outputs/samples_", tstamp, ".csv"), row.names=FALSE  )
write.csv( params_est[["savepar"]], paste0("outputs/params_", tstamp, ".csv"), row.names=FALSE )
write.csv( DAT, paste0("outputs/DAT_", tstamp, ".csv"), row.names = FALSE )
saveRDS( seir_2grp_tauleap, paste0("outputs/seir_2grp_tauleap_", tstamp, ".rds") )
```


